---
title: "p8105_hw6"
output:
  html_document: 
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```  


This is the homework 6 answer from Jian Zou (jz2924) and Hsiang Lun Kao (hk2968).  

## Describes the data used
In this page, we will briefly introduce how we create a flexdashboard and a shiny-enabled dashboard.  
The dataset used is **Instacart** which can be obtained at [The Instacart Online Grocery Shopping Dataset 2017](https://www.instacart.com/datasets/grocery-shopping-2017).  
15 columns are included in this dataset which is about shopping online from local stores.

## Relevant processing steps

### Import the data
```{r eval = FALSE}
library(tidyverse)
library(janitor)
library(stringr)
library(forcats)
library(viridis)
library(plotly)

instacart = read_csv("../data/instacart_train_data.csv.zip")
```  


### Number of items 
In this part, we rank the department according to number of items ordered. Users can choose the rank (e.g. top 10 departments).
```{r eval = FALSE}
renderPlotly({ 
  instacart %>%
  group_by(department) %>%
  summarize(items_ordered = n()) %>%
  mutate(depart_rank = min_rank(desc(items_ordered))) %>%
  arrange(depart_rank) %>%
  mutate(department = fct_reorder(department, items_ordered)) %>%
  filter(depart_rank %in% input$rank[1]:input$rank[2]) %>%
  plot_ly(y = ~items_ordered, x = ~department, type = "bar")
})
```


### Order hours for items
In this part, we use the "violin plot" to show the distribution of order hour in a day for each department.
```{r eval = FALSE}
renderPlotly({
  instacart %>%
  filter(department==input$obs) %>%
  mutate(department = fct_reorder(department, order_hour_of_day, IQR)) %>%
  ggplot(aes(x = department, y = order_hour_of_day, fill = department)) + 
  geom_violin(bw = .6) +
  theme(axis.text.x = element_text(angle = 90))
  })
```


### Mean order hour in a week
In this part, boxplot is adopted to show the distribution of mean order in a week.
```{r eval = FALSE}
mean_hour =
  instacart %>%
  group_by(product_name, order_dow) %>%
  summarize(mean_hour = mean(order_hour_of_day)) %>%
  spread(key = order_dow, value = mean_hour) %>%
  gather(key = day, value = mean_hour, "0":"6") %>%
  ggplot(aes(x = day, y = mean_hour, color = day)) +
  geom_boxplot()

ggplotly(mean_hour)
```  

## Related link
* [Flexdashboard](flexdashboard.html)
* [Rmd for the flexdashboard](https://github.com/jianzou95/1711111_p8105_hw6/blob/master/flexdashboard.Rmd)
* [Shiny](https://jianzou.shinyapps.io/shiny/)
* [Rmd for the shiny](https://github.com/jianzou95/1711111_p8105_hw6/blob/master/shiny.Rmd)
* [Github respository used to summarize this homework](https://github.com/jianzou95/1711111_p8105_hw6)